---
title: "linear model project"
author: "Jason Rivera"
date: "November 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sim = read.csv('sim.csv', header=TRUE)
attach(sim)

```

# Introduction
This data was taken from http://onlinestatbook.com/case_studies_rvls/physical_strength/index.html The data set contains observations from job applications on their sim score arm strength, grip and rating.

We write there models:

1. sims = f(arm)

2. sims = f(grip)

3. sims = f(arm,grip)

## First Model

```{r}
model1 = lm(SIMS~ARM)
# scatterplot
plot(ARM, SIMS)
abline(model1)
#numeric summary
summary.lm(model1)
```
This scatterplot shows the higher your arm strength the the higher your sim score but it is not entirely accurate.


The prediction interval for model 1 when arm=94, grip=88 is:

```{r}
newdata = data.frame(ARM=94, GRIP=88)
predict(model1, newdata, interval='prediction')
```

If your arm strength is 94 then we predict you'll have an average sim score between -1.401556 and 3.469079

## Second Model

```{r}
model2 = lm(SIMS~GRIP)
# scatterplot
plot(GRIP, SIMS)
abline(model2)
#numeric summary
summary.lm(model2)
```
This scatterplot shows that the stronger the grip the higher the sims, but its not entirely accurate.


The prediction interval for model 2 when arm=94, grip=88 is:

```{r}
predict(model2, newdata, interval='prediction')
```
If your grip score is 88 we predict your average sim score will be between -3.38434 and 1.766475


## Third Model

```{r}
model3 = lm(SIMS~ARM+GRIP)
#numeric summary
summary.lm(model3)
```
The p-value is 2.2e-16 which is less than 0.5 so we have evidence that arm strength is related to grip. 

```{r}
predict(model3, newdata, interval='prediction')
```

Having an arm strength of 94 and grip of 88 gives you and average sim score between -2.070793 and 2.524175

```{r}
anova(model1, model3)
```
model 3 is a better predictor using arm strength and grip than just using arm strength.

## Discussion and Conclusion
In our first model we discovered that measuring arm strength alone gets you a higher average sim score (-1.401556 and 3.469079) than the second model grip (-3.38434 and 1.766475), but the p-value of ARM + GRIP gives us a p-value of 2.2e-16 which is far less than 0.05. Giving us evidence that arm strength is related to grip. Also Measuring ARM+Grip (model3) is a better predictor of simulation scores than just ARM (model1)

